%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\usepackage{fontawesome}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADER SETINGS----------
\def \linkedinicon {\faLinkedin}
\def \linkedinlink {https://www.linkedin.com/in/thienlongtran}
\def \linkedintext {/thienlongtran}

\def \emailicon {\faEnvelope}
\def \emaillink {mailto:ttran384@gatech.edu}
\def \emailtext {ttran384@gatech.edu}

\def \githubicon {\faGithub}
\def \githublink {https://github.com/thienlongtran}
\def \githubtext {/thienlongtran}

\def \websiteicon {\faGlobe}
\def \websitelink {https://www.thienlongtran.com/}
\def \websitetext {/thienlongtran.com}

\def \phoneicon {\faPhone}
\def \phonelink {tel:346-204-9381}
\def \phonetext {(346)-204-9381}

\definecolor{LinkColor}{HTML}{3e70bb}

\def \linkedin {\linkedinicon\hspace{3pt}\textcolor{LinkColor}{\href{\linkedinlink}{\linkedintext}}}
\def \email {\emailicon\hspace{3pt}\textcolor{LinkColor}{\href{\emaillink}{\emailtext}}}

\def \github {\githubicon \hspace{3pt}\textcolor{LinkColor}{\href{\githublink}{\githubtext}}}

\def \website {\websiteicon\hspace{3pt}\textcolor{LinkColor}{\href{\websitelink}{\websitetext}}}

\def \phone {\phoneicon\hspace{3pt}\textcolor{LinkColor}{\href{\phonelink}{\phonetext}}}


%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Thien Tran} \\ \vspace{1pt}
    {\email} $|$ 
    {\phone} $|$ 
    {\website} $|$
    {\linkedin} $|$
    {\github}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{January 2022 - December 2023 (Expected)}
      {Master of Science in Computer Science - GPA: 4.0/4.0}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Knowledge-Based AI}
        
      \resumeItemListEnd
    \resumeSubheading
      {University of New Orleans}{August 2019 - December 2021}
      {Bachelor of Science in Computer Science - GPA: 4.0/4.0}{New Orleans, LA}
      \resumeItemListStart
        \resumeItem{\textbf{Leadership:} Google Developers Student Club (DSC Lead), Toastmasters (President), SGA (Senator)}
        %\resumeItem{\textbf{Honors: }President's List (All Semesters), Achievement in Computer Science Scholarship (2020-2021)}
        \resumeItem{\textbf{Relevant Coursework:} Data Structures \& Algorithms, Algorithm Analysis, Python for Data Science \& Artificial Intelligence, Database Management Systems, Cloud Computing, Computer Networks, Operating Systems}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}\hspace*{1cm}{Python, Java, HTML, CSS, JavaScript, SQL} \\
     \textbf{Technologies}\hspace*{0.6cm}{Git, Unity, Jupyter Notebook} \\
     %\textbf{Libraries}\hspace*{1.25cm}{NumPy, Pandas, Matplotlib, scikit-learn} \\
     \textbf{DevOps}\hspace*{1.4cm}{Amazon Web Services (AWS), Terraform, GitLab CI/CD} \\
     \textbf{Certifications}\hspace*{0.4cm}{AWS Solutions Architect - Associate, AWS Cloud Practitioner} 
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
     \resumeSubheading
      {PayPal}{May 2022 - August 2022}
      {Software Engineer Intern (DevOps)}{Austin, TX}
      \resumeItemListStart
      \resumeItem {Joining Venmo, a PayPal service, for an exciting and enriching experience this upcoming summer!}
      \resumeItem {Assisting the Platform Infrastructure Team with CI/CD migration from Jenkins to GitHub Actions.}
      \resumeItem {Increasing infrastructure reliability by fixing and enabling persistent synthetic tests on AWS EKS containers.}
    \resumeItemListEnd
    \resumeSubheading
      {USAA}{May 2021 - July 2021}
      {Software Engineer Intern (DevOps)}{Plano, TX}
    \resumeItemListStart
      \resumeItem {Reduced cluttering of a qTest archive by 84\% and allowed for easier feature-based auditing by designing a new directory structure for publishing automated infrastructure test results that affected 70 projects.}
      \resumeItem {Enabled automatic AWS resource tagging on one parameter if not provided by a developer or optional manual tagging otherwise by modifying a custom Terraform provider utilized by 55 projects using GoLang.}
      \resumeItem {Decreased the cost of conducting network connectivity testing on EC2 instances by 92.38\% by developing a selection of 5 AWS Systems Manager (SSM) testing automations using Terraform and GitLab CI/CD.}
      %\resumeItem {Developed a selection of 5 AWS Systems Manager (SSM) documents and automation using Terraform and GitLab CI/CD which reduced the time it takes to conduct network connectivity testing from 3-4 hours with 2-3 engineers to 35-45 minutes with a single engineer.}
    \resumeItemListEnd
    
    \resumeSubheading
      {University of New Orleans}{January 2021 - May 2021}
      {Undergraduate Research Assistant}{New Orleans, LA}
      \resumeItemListStart
        \resumeItem{Developed immersive eXtended Reality (XR) games using Unity and C\# under advisement of Dr. Farjana Eishita to discreetly detect 8 types of cognitive distortions and other mental health conditions.}
        \resumeItem{Converted 42 scenes of an existing cognitive distortion detection game manually from Augmented Reality (AR) to Mixed and Virtual Reality (MR \& VR) for player-experience (PX) comparisons between platforms.}
        \resumeItem{Conducted moderated PX testing on 9 individuals to identify bugs and ensure effective game-play engagement.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Stocks Simple Moving Average} $|$ \emph{Python, Amazon Web Services}}{}
          \resumeItemListStart
            \resumeItem{Developed an AWS pipeline that computes the Simple Moving Average (SMA) of historical OHLC-type stocks.}
            \resumeItem{Created the cloud infrastructure using the AWS Python SDK (Boto3) to automatically initialize and connect two S3 buckets, two Lambda functions, one SNS topic, and one DynamoDB NoSQL database table.}
            \resumeItem{Decreased the time it takes to acquire the SMA of an input file by 99.87\% compared to manual calculation.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Warframe Inventory Market Info} $|$ \emph{Python}}{}
          \resumeItemListStart
            \resumeItem{Developed a program that automatically gathers 4 different economic attributes about users’ in-game Warframe inventory items, saving users about 52 seconds of work per item page compared to manual calculation.}
            \resumeItem{Generated a list of inventory items using OpenCV to isolate item names from the inventory-screen image by thresholding the text colors, and by using PyTesseract to read and save the remaining text.}
            \resumeItem{Enabled better investment decisions and comparisons by collecting the average currency price of the 10 current cheapest live web market value sell-orders using the warframe.market API for each item in the generated item list.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
